---
title: "Highway Network"
author: "Jacob Ford DCHC MPO"
date: "4/5/2021"
output: html_document
---

## Highway Network

Finally, the existing highway network from the Triad was used as the basis for the highway network in Alamance County. Existing highway attributes from the Triad were coded into the TrueU for the TRM G2. Using InfoUSA and aerial mapping, existing links were added into the network as the team saw fit. The TRMv6.2, Triad, and TRM G2 highway networks, with centroid connectors removed, are viewable in the below map: 

```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
library(dplyr)
library(ggplot2)
library(leaflet)
library(tcadr)
library(sf)
library(xlsx)
library(readxl)
library(plotly)
library(sf)
library(dplyr)
library(tidygeocoder)
library(leaflet)
library(rgdal)
library(dplyr)
library(rmarkdown)
library(crosstalk)
library(lubridate)
library(htmltools)
library(RColorBrewer)


triad_hwy <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/TriadModel/MasterLnFiles/TriadHwy_Lines.shp")

triad_hwy <-triad_hwy %>%
  filter(triad_hwy$FACILITY_T!="Centroid Connector")

trm_v6_hwy<- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/TriadModel/MasterLnFiles/TRM_v6_hwy.shp")

trm_v6_hwy <- trm_v6_hwy %>%
  filter(trm_v6_hwy$SPECIAL!=31)

trm_g2_hwy<- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/TriadModel/MasterLnFiles/TRM_NG_HWY.shp")

trm_g2_hwy <- trm_g2_hwy %>%
  filter(trm_g2_hwy$B_SPECIAL!=31 | trm_g2_hwy$SPECIAL1!=31 |trm_g2_hwy$SPECIAL2!=31 |trm_g2_hwy$SPECIAL3!=31  )


```
```{r echo=FALSE, message=FALSE, warning=FALSE}
hwy_maps <-leaflet()%>%
  setView(-79.26, 36.05, zoom=11) %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addPolylines(data=trm_v6_hwy,
            group ="TRMv6.2",
            color="black",
            opacity=0.6,
            weight=0.5,
            popup=paste("Road Name: ", trm_v6_hwy$ROADNAME)) %>%
  addPolylines(data=triad_hwy,
               group="Triad",
               color="blue",
               opacity=06,
               weight=0.5,
               dashArray = "5,5",
               popup=paste("Road Name: ", triad_hwy$ROUTE_NAME)) %>%
    addPolylines(data=trm_g2_hwy,
               group="TRMG2",
               color="green",
               opacity=0.6,
               weight=0.5,
               popup=paste("Road Name: ", trm_g2_hwy$ROADNAME)) %>%
  
    addLayersControl(overlayGroups = c("TRMv6.2", "Triad", "TRMG2")) 


hwy_maps %>% hideGroup("TRMG2")
```


