---
title: "Socioeconomic and Demographic Data"
author: "Jacob Ford DCHC MPO"
date: "4/5/2021"
output: html_document
---



```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
library(dplyr)
library(ggplot2)
library(leaflet)
library(tcadr)
library(sf)
library(xlsx)
library(readxl)
library(plotly)
library(sf)
library(dplyr)
library(tidygeocoder)
library(leaflet)
library(rgdal)
library(dplyr)
library(rmarkdown)
library(crosstalk)
library(lubridate)
library(htmltools)
library(RColorBrewer)

#install.packages("kableExtra")
library(kableExtra)

triad_taz <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/Triad_TAZ.shp")

trm_taz <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TAZ_Shape.shp")

trmg2_taz <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/TRMG2_TAZ.shp")


```

## Overview

Existing data from both the TRMv6.2 and Triad Model were used for the TRM G2 expansion. Existing data from the TRMv6.2 for Orange County TAZs for both employment and demographic data was used, as the data represented the external boundary of the Triad model and overlapped into the existing TRM region, making for an easy transition. The remaining task for Orange County TAZs was to allocate the data to the new TAZs. InfoUSA point layer data allowed for total employment by category to be aggregated to the new TRM G2 TAZs, which would then serve as a factor against the original TRMv6.2 TAZ. Similarly, parcel level housing data was used to factor against the number of households and total population. 

For Alamance County, the Triad Model's existing demographic and employment data was used, and a similar factoring methodology was deployed. However, the transfer was more complicated as the TAZ boundaries differed between the TRM G2 and the Triad. A tool was developed to factor Triad data into TRM G2 available in an external google sheet, which accounts for not just InfoUSA and parcel level housing data but also total area covered. An example of the Triad SE data format is provided below for context:  




```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
triad_se <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/Triad Model/SE/SE 2017_v5_03-19-2019.bin")

triad_se_df <- triad_se[triad_se$COUNTY_NAME=="Alamance",]




triad_se_df %>%
  select(ID ,COUNTY_NAME,  HH, POP_GRP_QT, POP_IN_HH, EMP_HWYRET, EMP_IND, EMP_RETAIL, EMP_SERVICE, EMP_OFFICE,SCHOOL_EMP, K12_STUDENT)

triad_se_df <- head(triad_se_df, 10)


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
kbl(triad_se_df, caption="Triad Socioeconomic and Demographic Data (sample)") %>%
  kable_classic(html_font="Cambria")
```

## Employment Data

As previously mentioned, InfoUSA 2016 point data formed the distribution factor for employment data. The point layer is available below along with the TAZ boundaries for the TRMv6, TRM G2, and the Triad Model. 


```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}

orange_emp <-st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/SE Data/Employment/Mebane_OC_Employment_2016.shp")
alamance_emp <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/TRM G2/Alamance Expansion/SE Data/Employment/Mebane_AC_Employment_2016.shp")

```



```{r, echo=FALSE, message=FALSE, warning=FALSE}

map <- leaflet(data=triad_taz) %>%
  setView(-79.26, 36.05, zoom=11) %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addPolygons(data=triad_taz,
              group="Triad",
              color="red",
              fillColor = "lightgrey",
              weight=2,
             # fill=NA,
              dashArray = c("5,10"),
              popup=paste("Triad TAZ ID: ", triad_taz$TAZ)) %>%
    addPolygons(data=trm_taz,
              group="TRM",
              color="black",
              fillColor="blue",
              weight=1,
              popup=paste("TRM TAZ ID: ", trm_taz$TAZ_ID)) %>%
  addPolygons(data=trmg2_taz,
              group="TRMG2",
              color="green",
              weight=1,
              popup=paste("TRMG2 TAZ ID: ", trmg2_taz$TAZ_ID)) %>%
    addCircles(data=orange_emp,
             radius=orange_emp$EMP_2016RE,
             color="orange",
              group="Orange Employment",
              popup=paste("Company Name: ", orange_emp$COMPANY_NA, "<br>",
                          "TRM Employment Category: ", orange_emp$ESTAB_TYP2,"<br>",
                          "Employees: ", orange_emp$EMP_2016RE)) %>%
  addCircles(data=alamance_emp,
             radius=alamance_emp$ACTUAL_LOC,
             color="blue",
             fillColor ="blue",
             group="Alamance Employment",
             popup=paste("Company Name: ", alamance_emp$COMPANY_NA, "<br>",
                         "TRM Employment Category: ", alamance_emp$TRM_EMPLOY, "<br>",
                         "Employees: ", alamance_emp$ACTUAL_LOC)) %>%
  addLayersControl(overlayGroups = c("Triad", "TRM", "TRMG2", "Alamance Employment", "Orange Employment"))

map %>% hideGroup("Triad") %>% hideGroup("TRM")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

trm_taz_zoom <- trm_taz %>%
  filter(trm_taz$TAZ_ID==1208)

trmg2_taz_zoom <- trmg2_taz %>%
  filter(trmg2_taz$TAZ_ID==1208 | trmg2_taz$TAZ_ID==1377 )

map <- leaflet(data=triad_taz) %>%
  setView(-79.2, 36.06, zoom=14) %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
    addPolygons(data=trm_taz_zoom,
              group="TRM",
              color="black",
              fillColor="blue",
              weight=1,
              popup=paste("TRM TAZ ID: ", trm_taz_zoom$TAZ_ID)) %>%
  addPolygons(data=trmg2_taz_zoom,
              group="TRMG2",
              color="green",
              weight=1,
              popup=paste("TRMG2 TAZ ID: ", trmg2_taz_zoom$TAZ_ID)) %>%
    addCircles(data=orange_emp,
             radius=orange_emp$EMP_2016RE,
             color="orange",
              group="Orange Employment",
              popup=paste("Company Name: ", orange_emp$COMPANY_NA, "<br>",
                          "TRM Employment Category: ", orange_emp$ESTAB_TYP2,"<br>",
                          "Employees: ", orange_emp$EMP_2016RE)) %>%
  addCircles(data=alamance_emp,
             radius=alamance_emp$ACTUAL_LOC,
             color="blue",
             fillColor ="blue",
             group="Alamance Employment",
             popup=paste("Company Name: ", alamance_emp$COMPANY_NA, "<br>",
                         "TRM Employment Category: ", alamance_emp$TRM_EMPLOY, "<br>",
                         "Employees: ", alamance_emp$ACTUAL_LOC)) %>%
   addLabelOnlyMarkers(
    lng = -79.2071451, lat = 36.0658,
    label = "HH: 475  Pop: 1186 Employment: 43",
    labelOptions = labelOptions(noHide = T), group="TRMG2") %>%
    
  addLabelOnlyMarkers(
    lng = -79.1789591, lat = 36.0684597,
    label = "HH: 58 Pop: 145  Employment: 226",
    labelOptions = labelOptions(noHide = T), group="TRMG2") %>%
  addMarkers(
    lng = -79.1961044, lat = 36.0616725,
    label = "HH: 533 Pop: 1331  Employment: 269",
    labelOptions = labelOptions(noHide = T), group="TRM") %>%
  


  addLayersControl(overlayGroups = c("TRM", "TRMG2", "Alamance Employment", "Orange Employment"))

map %>% hideGroup("TRM")


```


















## Demographic Data

Where the employment data was distributed using InfoUSA point data, parcel data exported as centroids available from the respective county website were used as the distributive factor for number of households and population. To filter out commericial or non-residential homes, the parcel classification from county websites was used. Pin numbers are used at the home level to join parcel point data and parcel polygon layers from the county website, however only the final point layer is provided below. Home type classifications is available below when clicking on a point:  

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}


orange_parcel <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/Orange_Parcel_Points_v2.shp")

alamance_parcel <- st_read("C:/Users/JacobFo/OneDrive - City of Durham/Alamance_Parcel_Points.shp")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
parcel_map <-leaflet(data=alamance_parcel)%>%
  setView(-79.26, 36.05, zoom=11) %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addCircles(data=alamance_parcel,
            group ="Alamance Parcels",
             radius=alamance_parcel$AHBED_,
             color="green",
            popup=paste("Home Type: ", alamance_parcel$XXDDC1, "<br>")) %>%
  addCircles(data=orange_parcel,
            group="Orange Parcels", radius=2,
          color="orange",
          popup=paste("Home Type: ", orange_parcel$LBSCDESC)) %>%
    addPolygons(data=triad_taz,
              group="Triad",
              color="red",
              fillColor = "lightgrey",
              weight=2,
             # fill=NA,
              dashArray = c("5,10"),
              popup=paste("Triad TAZ ID: ", triad_taz$TAZ)) %>%
    addPolygons(data=trm_taz,
              group="TRM",
              color="black",
              fillColor="blue",
              weight=1,
              popup=paste("TRM TAZ ID: ", trm_taz$TAZ_ID)) %>%
  addPolygons(data=trmg2_taz,
              group="TRMG2",
              color="green",
              weight=1,
              popup=paste("TRMG2 TAZ ID: ", trmg2_taz$TAZ_ID)) %>%
  addLayersControl(overlayGroups = c("Triad", "TRM", "TRMG2", "Alamance Parcels", "Orange Parcels"))

parcel_map %>% hideGroup("TRM") %>% hideGroup("Triad")
```




```{r eval=FALSE, include=FALSE}
taz_tool <-leaflet()%>%
  setView(-79.26, 36.05, zoom=11) %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addPolygons(data=trmg2_taz,
              group="TRMG2",
              color="green",
              weight=1,
              popup=paste("TRMG2 TAZ ID: ", trmg2_taz$TAZ_ID))


taz_tool
```








```{r eval=FALSE, include=FALSE}
alamance_se <- trmg2_taz %>%
  filter(trmg2_taz$COUNTY=="Alamance")

head(alamance_se)

alamance_tazs <- unique(trmg2_taz$TAZ_ID[trmg2_taz$COUNTY=="Alamance"])

alamance_tazs <- sort(alamance_tazs[!is.na(alamance_tazs)])

alamance_df <- data.frame(matrix(ncol=9, nrow=nrow(alamance_se)))

col_names <- c("TAZ", "HH", "HH_Pop", "Ind", "Office", "SvcLo", "SvcHi", "Ret", "Total Employment")

colnames(alamance_df) <- col_names

alamance_df$TAZ <- (alamance_tazs)


head(alamance_df)

```






```{r eval=FALSE, include=FALSE}
alamance_df2 <- alamance_emp %>%
  filter(alamance_emp$TRM_TAZ>0)


alamance_df2$ACTUAL_LOC <- as.numeric(alamance_df2$ACTUAL_LOC)
sum(alamance_df2$ACTUAL_LOC, na.rm=T )

```







```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

for (taz in unique(alamance_df$TAZ)){
  
    alamance_df$`Total Employment`[alamance_df$TAZ==taz] <- sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz], na.rm=T)
    
    alamance_df$Ind[alamance_df$TAZ==taz] <- sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz & alamance_df2$TRM_EMPLOY=="Ind"], na.rm=T)
    alamance_df$Office[alamance_df$TAZ==taz] <- sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz & alamance_df2$TRM_EMPLOY=="Off"], na.rm=T)
    alamance_df$SvcLo[alamance_df$TAZ==taz] <- sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz & alamance_df2$TRM_EMPLOY=="SvcLo"], na.rm=T) +     sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz & alamance_df2$TRM_EMPLOY=="SvcHi"], na.rm=T)
    
    alamance_df$SvcHi[alamance_df$TAZ==taz] <- NA
    alamance_df$Ret[alamance_df$TAZ==taz] <- sum(alamance_df2$ACTUAL_LOC[alamance_df2$TRM_TAZ==taz & alamance_df2$TRM_EMPLOY=="Ret"], na.rm=T)
    
  
  
}

alamance_df

```

## Final Conversion Table

The conversion sheet linked below allows for Triad SE data to be converted into the relevant TRM G2 data. Note, that refinements were required to control for TAZs that hold only retail shopping for example. 

[Triad to TRM Conversion Sheet](https://drive.google.com/file/d/1a783Js4Y3pwKLMTg7rOvv8GCIGdmPZEY/view?usp=sharing)












